\section{Mechanical Design and Enclosure}
\label{sec:mechanical_design}

\subsection{Light Tube Enclosure V2}
\label{subsec:light_tube_enclosure_v2}
\begin{itemize}
	\item Describe the design of the Light Tube enclosure using aluminum profiles and 3D printed end caps or mounting elements.
	\item Discuss the selection of aluminum profiles (e.g., size, shape).
	\item Detail the design and manufacturing process of the 3D printed parts.
	\item Mention any design considerations (e.g., light diffusion, mounting options, cable management).
\end{itemize}

\subsection{Light Tube Enclosure V3}
\label{subsec:light_tube_enclosure_v3}
\begin{itemize}
	\item Describe the design of the Light Tube enclosure using aluminum profiles and 3D printed end caps or mounting elements.
	\item Discuss the selection of aluminum profiles (e.g., size, shape).
	\item Detail the design and manufacturing process of the 3D printed parts.
	\item Mention any design considerations (e.g., light diffusion, mounting options, cable management).
\end{itemize}

\subsection{Panel Enclosure}
\label{subsec:panel_enclosure}
\begin{itemize}
	\item Describe the design of the Panel enclosure, primarily using 3D printed parts.
	\item Detail the design and manufacturing process of the 3D printed enclosure components.
	\item Mention any design considerations (e.g., rigidity, mounting options, heat dissipation).
\end{itemize}

\subsection{Spotlight Enclosure}
\label{subsec:spotlight_enclosure}
\begin{itemize}
	\item Describe the design of the Spotlight enclosure, primarily using 3D printed parts, including the 60° focusing mechanism.
	\item Detail the design and manufacturing process of the 3D printed enclosure components and the focusing element.
	\item Mention any design considerations (e.g., light focusing accuracy, heat dissipation, mounting options).
\end{itemize}

\subsection{Connection System \enquote{click \& hope}}

\subsection{Connection System \enquote{screw it!}}

\subsection{3D Printing}

\subsubsection{Light Tube V2 Parts}

\subsubsection{Light Tube V3 Parts}

\subsubsection{Panel Parts}

\subsubsection{Spotlight Parts}

\subsubsection{Connection System Parts}